Hierarchically Supervised Latent Dirichlet Allocation

### 2011-05-22 paper/abstract.tex
a first draft (sucky) abstract and introduction

We introduce hierarchically supervised latent Dirchlet allocation (HSLDA), a model for hierarchically and multiply labeled bag-of-words data.  Out-of-sample label prediction is the primary goal of this work; however, improved dimensionality reduction is also of interest.  We define a model that uses probit regressors on a conditionally dependent label hierarchy tied to latent Dirichlet allocation (LDA) in the same manner as was done in supervised LDA (SLDA) prior art.  We find that the additional supervision signal that comes from multiple, hierarchically constrained labels substantially improves out-of-sample label prediction in medical document labeling and product categorization tasks.  Additionally, held-out likelihood

>>>>

We introduce hierarchically supervised latent Dirchlet allocation (HSLDA), a model for hierarchically and multiply-labeled bag-of-words data.  Out-of-sample label prediction is the primary goal of this work; however, improved dimensionality reduction is also of interest.  We define a model that uses probit regressors on a conditionally dependent label hierarchy tied to latent Dirichlet allocation (LDA).  We find that the additional signal that comes from multiple, hierarchically constrained labels substantially improves out-of-sample label prediction in comparison to supervised LDA approaches that don't utilize information derived from the structure of the label space.   We demonstrate HSLDA on large-scale data from medical document labeling and retail product categorization tasks and show both improved label prediction performance and show evidence that the learned topic model improves as a result of using this signal too.

### 2011-05-22 paper/main.tex
added figures to tex.  win!
a first draft (sucky) abstract and introduction

\section{Methods}
\label{sec:methods}

@@

\subsection{Posterior Inference}

@@

\subsection{Gibbs Sampling}

@@

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{Combined_vs_Separate_Learning.png}
\caption{default}
\label{default}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{TP_Rate.png}
\caption{default}
\label{default}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{FP_Rate.png}
\caption{default}
\label{default}
\end{center}
\end{figure}

>>>>

\section{Model}
\label{sec:model}

@@

\section{Inference}
\label{sec:inference}

@@

\subsection{Gibbs Sampler}

@@

\subsection{Evaluation}

@@

\begin{figure}[htbp]
\begin{center}
\subfigure[]{\includegraphics[width=.49\textwidth]{figs/ROC_comparison_ancestors}}
\subfigure[]{\includegraphics[width=.49\textwidth]{figs/ROC_comparison_leafs}}
\subfigure[]{\includegraphics[width=.49\textwidth]{figs/sens_comparison_leafs}}
\subfigure[]{\includegraphics[width=.49\textwidth]{figs/one_m_spec_comparison_leafs}}
\caption{Out-of-sample ICD-9 code prediction from patient free-text discharge records.  In all figures solid is HSLDA, dashed is ADLER, dotted is ADLER, and dot-dashed is ADLER.}
\label{fig:icd9}
\end{center}
\end{figure}
